Tables

### 2019-05-16 code/tables.rmd
Changed tau2 to tau in table 3

res <- res %>%
  mutate(tau2 = res2$tau2, #For table 3, report tau2 and transformed effect sizes (biserial correlations)
         tau2_ci.lb = res2$tau2.lb,
         tau2_ci.ub = res2$tau2.ub,
         r = res2$r)

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_power) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(tau2_ci.ub, 2), nsmall = 2)), "]")) %>% 
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau2, tau2_ci, zero, small, medium, large)

@@

##Table 3
###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
```{r heterogeneity-table, cache = TRUE}
#library(kableExtra)

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "r*" , "$\\tau^2$", "$\\tau^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 10, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 10, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, K = no. primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations. $I^2$ and its confidence intervals are for original effect size specifications whereas $/tau^2$ and its confidence intervals are for transformed r* effect sizes. Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences") %>% 
  landscape()

>>>>

res <- res %>%
  mutate(tau = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
         tau_ci.lb = sqrt(res2$tau2.lb),
         tau_ci.ub = sqrt(res2$tau2.ub),
         r = res2$r)

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_power) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 4), nsmall = 4)), ", ", trimws(format(round(tau_ci.ub, 4), nsmall = 4)), "]"),
         tau = format(round(tau, 4), nsmall = 4)) %>% #rounded here instead of in table function because should have 4 digits
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau, tau_ci, zero, small, medium, large)

@@

```{r heterogeneity-table, cache = TRUE}
#library(kableExtra)

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "r*" , "$\\tau$", "$\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 10, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 10, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, K = no. primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations. $I^2$ and its confidence intervals are for original effect size specifications whereas $/tau^2$ and its confidence intervals are for transformed r* effect sizes. Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences") %>% 
  landscape()
